SoK: Transparent Dishonesty: front-running attacks on Blockchain.

### 2019-01-17 frontrunning/Latex/sections/paper.tex
[frontrunning] add a text/comment regarding ERC20 approve frontrunning

As seen in traditional financial markets, one method to manipulate the spot price of an asset, is to flood the market with orders and cancel them when there are filling orders (``taker's griefing''~\cite{consesnsys0xReview2017}). Placing an order in a partially centralized exchange is free, but to prevent taker's griefing attacks, the user needs to send an Ethereum transaction to cancel each of his orders. Cancelling orders is most important when prices change faster than order execution. In this case, when an adversarial actor sees a pending cancellation transaction, he sends a fill order transaction with higher gasPrice to get in front of the cancellation order and take the order before it is canceled (this is known as \textit{cancellation grief}). This attack follows the (asymmetric) insertion template and is illustrated in Figure~\ref{fig:MinerFrontrunning}.

>>>>

As seen in traditional financial markets, one method to manipulate the spot price of an asset, is to flood the market with orders and cancel them when there are filling orders (``taker's griefing''~\cite{consesnsys0xReview2017}). Placing an order in a partially centralized exchange is free, but to prevent taker's griefing attacks, the user needs to send an Ethereum transaction to cancel each of his orders. Cancelling orders is most important when prices change faster than order execution. In this case, when an adversarial actor sees a pending cancellation transaction, he sends a fill order transaction with higher gasPrice to get in front of the cancellation order and take the order before it is canceled (this is known as \textit{cancellation grief}). This attack follows the (asymmetric) insertion template and is illustrated in Figure~\ref{fig:MinerFrontrunning}. %Similarly, a front-running attack on ERC20 standard~\cite{erc20}, is on the allowance functionality, this allows a second entity to be able to spend N tokens from the owners balance. This attack is possible when the owner changes the allowance by calling a function \textit{approve()}, an attacker can front-run this transaction to allow herself to spend the allowance before the change replace the new allowance. There has been a few proposals to fix this issue, however some of them simply move the attack vector to another function. \\ citations: https://blog.smartdec.net/erc20-approve-issue-in-simple-words-a41aaf47bca6 , https://github.com/OpenZeppelin/openzeppelin-solidity/issues/437
